\Large \bf Byteboy : A Byteman Companion Application

### 2017-12-04 final-paper/paper.la_.tex
feat(paper): added references to the latex file

>>>>

\begin{thebibliography}{99}

\bibitem{bytemanwebsite} 
Byteman: Simplify Java tracing, monitoring and testing with Byteman,
\\\texttt{http://byteman.jboss.org/}

\bibitem{bytemanguide}
Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
\\\texttt{http://downloads.jboss.org/byteman/3.0.10/ProgrammersGuide.html}

\bibitem{yo}
Yo Code - Extension Generator
\\\texttt{https://code.visualstudio.com/docs/extensions/yocode}

\bibitem{textmate}
Textmate: Language Grammars
\\\texttt{https://manual.macromates.com/en/language\_grammars}

\bibitem{bytemanvideo}
Dinn, Andrew. \\\textit{Monitoring Application-Specific Behavior Using Thermostat and Byteman}
YouTube. 2016. URL: \\\texttt{https://www.youtube.com/watch?v=teL7qnulUTM}

\end{thebibliography}
